parental migration and adolescents educational performance

### 2022-06-12 data/Gu-thesis-script.Rmd
Scales package for min-max rescaling

```{r}
d1 <- d1 %>% group_by(clsids) %>%
  mutate(
    w1ttl_max = max(w1ttl, na.rm = T),
    w1ttl_min = min(w1ttl, na.rm = T),
    w2ttl_max = max(w2ttl, na.rm = T),
    w2ttl_min = min(w2ttl, na.rm = T),
    w1ttl_100_mean = mean(w1ttl_100, na.rm = T),
    w2ttl_100_mean = mean(w2ttl_100, na.rm = T)
  ) %>% ungroup()
d1 <- d1 %>%
  mutate(
    w1ttl_std = (w1ttl - w1ttl_min)/(w1ttl_max - w1ttl_min),
    w2ttl_std = (w2ttl - w2ttl_min)/(w2ttl_max - w2ttl_min),
    w1ttl_100_dm = (w1ttl_100 - w1ttl_100_mean),
    w2ttl_100_dm = (w2ttl_100 - w2ttl_100_mean)
  )
```

@@

t-test
```{r}
t.test(cog_dif ~ migr, data = d_cl)
t.test(ttl_dif ~ migr, data = d_cl)
t.test(chn_dif ~ migr, data = d_cl)
t.test(mat_dif ~ migr, data = d_cl)
t.test(eng_dif ~ migr, data = d_cl)
```

@@

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

>>>>

```{r}
d1 <- d1 %>% group_by(clsids) %>%
  mutate(
    w1ttl_std1 = rescale(w1ttl),
    w2ttl_std1 = rescale(w2ttl)
    ) %>% ungroup()
```

```{r}
d1 <- d1 %>% group_by(clsids) %>%
  mutate(
    w1ttl_100_mean = mean(w1ttl_100, na.rm = T),
    w2ttl_100_mean = mean(w2ttl_100, na.rm = T)
  ) %>% ungroup()
d1 <- d1 %>%
  mutate(
    w1ttl_std = (w1ttl - w1ttl_min)/(w1ttl_max - w1ttl_min),
    w2ttl_std = (w2ttl - w2ttl_min)/(w2ttl_max - w2ttl_min),
    w1ttl_100_dm = (w1ttl_100 - w1ttl_100_mean),
    w2ttl_100_dm = (w2ttl_100 - w2ttl_100_mean)
  )
```

@@

t-test
```{r}
t.test(cog_dif ~ migr, data = d_cl)
t.test(ttl_dif ~ migr, data = d_cl)
t.test(ttl_dm_dif ~ migr, data = d_cl)
```

@@
